How predictable is extinction?

### 2018-10-31 doc/gsa2018_talk.tex
full talk draft to send to SETH

  \begin{center}
    \begin{tabular}[c]{ p{2cm} c | p{2cm} | p{2cm} |}
      \cline{3-4} 
      & & \multicolumn{2}{ c |}{Actual class} \\ \cline{3-4}
      & & 1 & 0 \\ \hline
      \multicolumn{1}{| c |}{\multirow{2}{*}{Predicted class}}
      & 1 & TRUE \newline POSITIVE & FALSE \newline POSITIVE \\ \cline{2-4}
      \multicolumn{1}{| c |}{} & 0 & FALSE \newline NEGATIVE & TRUE \newline NEGATIVE \\
      \hline
    \end{tabular}
  \end{center}

  \begin{center}
    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{figure/wiki_ROC_space-2}
  \end{center}

@@

@@

@@

% demonstrate as ROC curve
\begin{frame}
  \frametitle{In-sample predictive performance, full dataset}

  \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/roc_hist}

@@

  \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/roc_ts}

@@

  \begin{itemize}
    \item \alert{The past matters\dots} 
      \begin{itemize}
        \item Our best supported model includes our historical covariates and allows all effects to vary over time.
      \end{itemize}
    \item \alert{But not that much\dots}
      \begin{itemize}
        \item None of our models are good at predicting extinction.
      \end{itemize}
    \item<2-> Mechanisms behind changes to geographic range operate at sub-million year scales. Perhaps their effects are weak/masked at million (or greater) year scales.
  \end{itemize}

@@

\begin{frame}
  \frametitle{Acknowledgements}

>>>>

  \begin{center}
    \includegraphics[width=\textwidth,height=0.75\textheight,keepaspectratio=true]{figure/confusion_matrix_wiki}
  \end{center}

@@

\end{frame}
%
%
%\begin{frame}
%  \frametitle{Measuring performance: Receiver Operating Characteristic}
%
%  \begin{center}
%    \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{figure/wiki_ROC_space-2}
%  \end{center}
%  
%  \attrib{\footnotesize{wikimedia}}
%
%\end{frame}

@@

\begin{frame}
  \frametitle{Measuring performance: AUC ROC}

  \begin{columns}
    \begin{column}{0.4\textwidth}
      \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{figure/AUC}

      \attrib{\footnotesize{https://goo.gl/91nEpM}}

    \end{column}
    \begin{column}{0.6\textwidth}
      \[
        \text{AUC} = 
        \begin{cases} 
          0.5 & \text{non discrimination}\\
          0.6-0.7 & \text{poor} \\
          0.7-0.8 & \text{acceptable/fair} \\
          0.8-0.9 & \text{excellent/good} \\
          > 0.9 & \text{outstanding} \\
        \end{cases}
      \]

      The area represents the probability of correct ranking of a random ``extinct''-``extant'' pair.
    \end{column}
  \end{columns}

@@

% demonstrate as ROC curve?
\begin{frame}
  \frametitle{In-sample predictive performance, full dataset}

  \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/auc_hist}

@@

  \includegraphics[width=\textwidth,height=0.8\textheight,keepaspectratio=true]{../results/figure/auc_ts}

@@

  \begin{itemize}
    \item \alert{The past matters\dots} 
      \begin{itemize}
        \item Our best supported model includes our historical covariates and allows all effects to vary over time.
      \end{itemize}
    \item \alert{But not that much\dots}
      \begin{itemize}
        \item None of our models are good at predicting extinction.
      \end{itemize}
    \item Perhaps mechanisms behind changes to geographic range operate at sub-million year scales. Perhaps their effects are weak/masked at million (or greater) year scales.
  \end{itemize}

@@

\begin{frame}
  \frametitle{Acknowledgements}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item \textbf{Seth Finnegan}
        \item Adiel Klompmaker 
        \item Emily Orzechowski
        \item Larry Taylor
        \item Sara Kahanamoku
        \item Josh Zimmt
        \item Franziska Franeck \\(University of Oslo)
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{center}
        \includegraphics[height=0.15\textheight,width=\textwidth,keepaspectratio=true]{figure/github-logo}

        psmits.github.io/ \hspace*{0.05\textwidth} \textbf{trident}
      \end{center}
      \vspace*{0.02\textheight}
      \begin{center}
        \includegraphics[height=0.1\textheight,width=0.5\textwidth,keepaspectratio=true]{figure/twitter}

        @PeterDSmits
      \end{center}
      \vspace*{0.02\textheight}
      \begin{center}
        \includegraphics[height=0.25\textheight,width=\textwidth,keepaspectratio=true]{figure/INAlogo}
      \end{center}
    \end{column}
  \end{columns}
\end{frame}
